outline!

### 2016-05-23 paper.tex

\documentclass[10pt,twocolumn]{article}
\usepackage{times}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage{subcaption}
\usepackage{graphicx,grffile}
\usepackage{pgf}
\usepackage{tikz}
\usepackage{listings}
\usepackage{color}
\usetikzlibrary{arrows,automata}
%\usepackage[latin1]{inputenc}

@@

\subsection{Optimization}

In this section we have demonstrated that a design based on an N:1 addressing
scheme that stores both log entries and metadata in the bytestream can provide
the best overall performance, and it does so by a large margin. However, this
process of design we have outlined may not yield such clear cut results when
applied in a different context.

To illustrate this we ran the same benchmark that measures expected append
throughput shown in Figure~\ref{fig:vanilla_wr_jewel} on identical hardware
but we used a long-term support version of Ceph released two years
ago. The result of this benchmark is shown in Figure~\ref{fig:vanilla_wr_firefly}
in which the bytestream interface outperforms the key-value interface by 12\%,
compared to over 100\% in the newer versino of Ceph. Qualatatively, given the
reduced overall throughput achieved in the older version, some developers may
find that incurring the overhead of using the key-value interface is an easy
decision given the reduced complexity of the design space for metadata
management. If this choice had been made, then a future system upgrade could
drop a significant number of iops on the floor.

In practice the real world state space is much larger than the one described
in this section. Ceph alone has hundreds of configuration options, significant
features becoming available with releases each year, and is designed to run on
a wide variety of COTS hardware as well as new NVMe devices, all of which
contribute to a large and dynamic state space. Application-level designs
also contribute to an expanded design space. In the N:1 design of mapping
CORFU onto Ceph the potential amount of I/O parallelism is controlled by 
the value N, however if this value becomes too large there may be no benefit
or performance could suffer from reduced data locality. Other aspects of
application-level design are even more flexible. A wide variety of data
structures could be serialized into the byte stream to handle metadata
management tasks, but selecting a single external index that performs well
across workloads and hardware may not be possible.

>>>>

\documentclass[10pt,twocolumn]{article}
\usepackage{times}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{graphicx,grffile}
\usepackage{pgf}
\usepackage{tikz}
\usepackage{listings}
\usepackage{color}
\usetikzlibrary{arrows,automata}
%\usepackage[latin1]{inputenc}

@@

Application-level designs also contribute to an expanded design space.  In the
N:1 design of mapping CORFU onto Ceph the potential amount of I/O parallelism
is controlled by the value N, however if this value becomes too large there may
be no benefit or performance could suffer from reduced data locality. Other
aspects of application-level design are even more flexible. A wide variety of
data structures could be serialized into the byte stream to handle metadata
management tasks, but selecting a single external index that performs well
across workloads and hardware may not be possible.

\subsection{Cluster-Specific Optimizations}

In this section we have demonstrated that a design based on an N:1 addressing
scheme that stores both log entries and metadata in the bytestream can provide
the best overall performance, and it does so by a large margin. However, this
process of design we have outlined may not yield such clear cut results when
applied in a different context. To illustrate the complexity and breadth of
this design space, we describe the software, system tunables, and hardware
parameters that affect the performance of ZLog.

\subsubsection{Software Parameters}

Ceph releases stable versions every year (Oct/Nov) and LTS versions every 3-4
months~\cite{website:ceph-releases}. The head of the master branch moves
quickly because there are over 400 contributors and an active mailing list.
Over the calendar year, there were between  70 and 260 commits per
week~\cite{website:ceph-github}. These releases contain performance fixes and
new features that could directly ZLog.

\textbf{Ceph Versions}: to show the affect that this has on ZLog's design, we
ran the same benchmark that measures expected append throughput shown in
Figure~\ref{fig:vanilla_wr_jewel} on identical hardware but instead use a
long-term support version of Ceph released two years ago. The result of this
benchmark is shown in Figure~\ref{fig:vanilla_wr_firefly} in which the
bytestream interface outperforms the key-value interface by 12\%, compared to
over 100\% in the newer version of Ceph. Qualitatively, given the reduced
overall throughput achieved in the older version, some developers may find that
incurring the overhead of using the key-value interface is an easy decision
given the reduced complexity of the design space for metadata management. If
this choice had been made, then a future system upgrade could drop a
significant number of iops on the floor.

\textbf{Ceph Features}: to show the affect of cutting-edge Ceph features, we
now show results for BlueStore~\cite{weil:vault2016-bluestore}. BlueStore is a
replacement for the FileStore file system in the OSD (traditionally XFS).
FileStore has performance problems with transactions and enumerations; namely
the journal needed to assure atomicity incurs double writes and the file system
metadata model makes object listings slow, respectively. BlueStore stores data
directly on a block device and the metadata in RocksDB, which is provided by a
minimalistic, non-POSIX C++ filesystem. This model adheres to the overall
software defined storage strategy of Ceph because it gives the administrator
the flexiblity to store the 3 componenets of BlueStore (e.g., data, RocksDB
database, and RocksDB write-ahead log) on any partition on any device in the
OSD.

\subsubsection{System Tunables}

The most recent version of Ceph (v10.2.0-1281-g1f03205) has 994 tunable
parameters\footnote{This number comes from \texttt{src/common/config\_opts.h}
with debug options filtered out.}, where 195 of them pertain to the OSD itself
and 95 of them focus on the OSD back end file system (i.e. its
\texttt{filestore}). Ceph also has tunables for the subystems it uses, like
LevelDB (10 tunables), RocksDB (5 tunables), its own key-value stores (5
tunables), its object cache (6 tunables), its journals (24 tunables), and its
other optional filestores like BlueStore (49 tunables).

This many domain-specific tunables makes it almost impossible to come up with
the best set of tunables, although auto-tuning like the work done
in~\cite{behzad:sc2013-autotuning} could go a long way. Regardless of the
technique that we use, it is clear the the number of tunables increases the
physical design parameters to an unwieldy stae space size.

\subsubsection{Hardware Parameters}

Ceph is designed to run on a wide variety of commodity hardware as well as new
NVMe devices, all of which their own set of characteristics and tunables (e.g.,
the IO operation scheduler type). In our experiments, we tested SSD, HDDs, NVMe
devices, and

\subsection{Discussion}

This physical design process, of first thinking about the design trade-offs and
then doing parameters sweeps, is insufficient when general-purpose systems. Had
we built ZLog from the ground up (like CORFU) the story might be different but
to deal wtih the large state space we need a way to automatically and
autonomically decide which parameters to choose.
